DATA 621 - Business Analytics and Data Mining

### 2020-11-25 Final_project/Draft_EDA_start.Rmd
Adding to the EDA

```{r libraries}
library(tidyverse)
library(tidymodels)
library(data.table)
library(corrplot)
library(vip)
library(psych)
library(summarytools)
library(readr)
library(knitr)
library(GGally)
```

@@

# Data
•Description of Data
–A complete description of the desired output

@@

~discuss using Excel for data cleaning for unique values in France.

```{r ca_data_prep}
ca_set <- ca_set %>% filter(complete.cases(ca_set))

ca_mean <- mean(ca_set$views)

ca_set <- ca_set%>%
  mutate(country = 'CA')%>%
  mutate(country_code = 1)%>%
  mutate(view_target = ifelse(views > ca_mean,1,0))%>%
  mutate(tag_count = 1+(str_count(ca_set$tags, ';')))
```

@@

```{r merge_datasets}
mergeCols = c('video_id','trending_date','title','channel_title','category_id','publish_time','tags','views','likes','dislikes','comment_count','thumbnail_link','comments_disabled','ratings_disabled','video_error_or_removed','description','country','country_code', 'view_target','tag_count')

full_set <- ca_set %>% full_join(de_set, by=mergeCols)
full_set <- full_set %>% 
  full_join(fr_set, by=mergeCols)%>%
  full_join(gb_set, by=mergeCols)%>%
  full_join(us_set, by=mergeCols)

full_mean <- mean(full_set$views)

full_set <- full_set %>%
  mutate(view_global_target = ifelse(views > full_mean,1,0))
```

```{r global_target}
ca_set <- ca_set %>%
  mutate(view_global_target = ifelse(views > full_mean,1,0))

@@

# Models
•Data Analysis
–Describe the instrumentation
–Describe the analysis plan
•Describe the scope and limitations of the methodology
## Model Creation

@@

### Criteria
### Performance

### Predictions

# Results
– Needs to systematically and clearly articulate the study findings. If the results are unclear, the reviewer must decide whether the analysis of the data was poorly executed or whether the Results section is poorly organized.

– Should state wheather the hypothesis were verified or proven untrue or, if no hypotheses were given, weather the research questions were answered.
The authors should also comment on their results in light of previous studies and explain what differences (if any) exist between the findings and those reported by others and attempt to provide an explaination of the differnces.

>>>>

```{r libraries}
library(tidyverse)
library(tidymodels)
library(data.table)
library(corrplot)
library(vip)
library(psych)
library(summarytools)
library(readr)
library(knitr)
library(GGally)

set.seed(951)
```

@@

# Data

@@

The owner of the dataset seemed to combine the five countries in question into the 
France dataset. Unfortunately, when this operation occurred, the owner left no marker 
in the dataset to identify which country the data came from originally.  As we are 
going to use the country as predictor, we needed to find a method to remove the unwanted 
values.

Using Excel, we performed a simple VLOOKUP on the video ID from the France dataset to 
the other four datasets.  If the Video ID was in another dataset, we flagged and removed 
it.  The resulting shortened dataset matched in item count to the other datasets.  As 
the datasets are static and we do not plan to have then constantly updated with fresh 
data, using the quickest simplest method is appropriate.

As each dataset is over 30,000 individual objects, incomplete cases were dropped completely. 
Out of the 40,881 objects in the raw Canada dataset, removing the incomplete cases only 
removed 1,296 (roughly 3.2%).  France had the highest number removed for incomplete cases 
at 8.1% and US being the lowest at 1.4%.  France being the highest is understandable due 
to the prior state of the dataset discussed earlier.

Summary statistic markers were calculated for each dataset and for the environment as a 
whole.

  * A country code (1-5) was applied to each dataset.  
  * Target values of view_target and view_target_global were created 
    * A value of '1' designates the view count is above the mean of the country 
      and global respectively. 
    * A value of '0' designates the view count falls below the mean respectively 
  * 'tag_count', A predictor value, was calculated by counting the number of tags applied 
    to each video entry.

```{r ca_data_prep}
# remove incomplete cases
ca_set <- ca_set %>% filter(complete.cases(ca_set))

#Calculating the mean of the CA dataset
ca_mean <- mean(ca_set$views)

ca_set <- ca_set%>%
  mutate(country = 'CA')%>% #Add country label
  mutate(country_code = 1)%>% #Add country code
  mutate(view_target = ifelse(views > ca_mean,1,0))%>% #calculate above/below view mean
  mutate(tag_count = 1+(str_count(ca_set$tags, ';'))) #count number of tags
```

@@

```{r merge_datasets}
# Prep column names for joins
mergeCols = c('video_id','trending_date','title','channel_title','category_id','publish_time','tags','views','likes','dislikes','comment_count','thumbnail_link','comments_disabled','ratings_disabled','video_error_or_removed','description','country','country_code', 'view_target','tag_count')

# Join the datasets into a single dataset
full_set <- ca_set %>% full_join(de_set, by=mergeCols)
full_set <- full_set %>% 
  full_join(fr_set, by=mergeCols)%>%
  full_join(gb_set, by=mergeCols)%>%
  full_join(us_set, by=mergeCols)

# Calculate Global mean
full_mean <- mean(full_set$views)

#calculate above/below global mean
full_set <- full_set %>%
  mutate(view_global_target = ifelse(views > full_mean,1,0))
```

```{r global_target}
# add global mean calculation to individual datasets
ca_set <- ca_set %>%
  mutate(view_global_target = ifelse(views > full_mean,1,0))

@@

# Models
•Data Analysis
–Describe the instrumentation
–Describe the analysis plan
•Describe the scope and limitations of the methodology

```{r}
#potential train/test split
ca_set_model <- ca_set %>%
  select(-title, -tags, -channel_title, -trending_date, -publish_time, -video_id, -thumbnail_link, -description, -country)

ca_smp_size <- floor(0.75*nrow(ca_set))
ca_ind <- sample(seq_len(nrow(ca_set)), size = ca_smp_size)

ca_train <- ca_set[ca_ind,]
ca_test <- ca_set[-ca_ind,]
```

## Model Creation
• describe which model are created and why

@@

### Criteria
• criteria of the model selection

### Performance
• describe the performance of the selection

### Predictions
• describe the prediction values

# Results
•Needs to systematically and clearly articulate the study findings. If the results are unclear, the reviewer must decide whether the analysis of the data was poorly executed or whether the Results section is poorly organized.

• Should state wheather the hypothesis were verified or proven untrue or, if no hypotheses were given, weather the research questions were answered.
The authors should also comment on their results in light of previous studies and explain what differences (if any) exist between the findings and those reported by others and attempt to provide an explaination of the differnces.
